Compilation with Dynamic Grammars

### 2019-09-07 papers/paper.tex
Fixes an ancient typo

Additionally, Glossa should provide a famework for creating programming languages.
This is done using the translation interface, where syntax of a new language is described with files, and the language is translated either to machine code, or another programming language which will later be compiled.

@@

assignment: `@lval identifier **` `@op '='` `@rval boolexpression | expression`
\end{verbatim}

@@

A transformer file is just a series of these transformations:
\begin{verbatim}
createreg [name]
// Copy an element from global multisymbol table to a key in a register's multisymbol table
transfer(-append) [reg-name] [global-key] [reg-key] 
// Move the multisymbol from a register to the destination key in the multisymbol table. 
// If a destination_reg is specified, this table is the table of a register. 
// Otherwise, it is the global multisymbol table
pushback(-override) [reg-name] [destination] (optional)[destination_reg]
// Prefix for performing an operation on a register
reg [name] {command (any of below)}

// The following also work with operations on the table of the current multisymbol
// In add and append, type might be "identifier" or "literal" 
//                              and value might be "x" or "2"
// I.e to add an identifier foo under the key "name", 
//   use the command (add name identifier foo)
// Add overwrites a key, append adds onto it.
add    [key] [type] [value]
append [key] [type] [value]
// Move deletes the source key, copy does not.
copy(-append) [key1] [key2]
move(-append) [key1] [key2]
// Change the tag of the register
retag newtag
// Delete a key from the multisymbol table
delete [key]
\end{verbatim}
Which can be surrounded by control flow, in the same way that constructor files can:
\begin{verbatim}
branch defined identifier 
move identifier old_identifier
add name identifier f
elsebranch
add name identifier f
end
\end{verbatim}
(This AST transform renames the syntax element to f, saving the old name to the key "old\_identifier"

@@

For example, adding a function to a particular programming language takes a single line:
\begin{verbatim}
function: 'def' `@name identifier **` '(' `@args sep ',' identifier **` ')' ':' `@body *statement` 'end'
\end{verbatim}
To change this Python style function to one in Haskell:
\begin{verbatim}
function: `@name identifier **` `@args sep SPACE identifier **` '=' `@body return` 'end'
\end{verbatim}
Since these two parsers define the same fields (name, args, body), they would be compiled in identical ways.

>>>>

Additionally, Glossa should provide a framework for creating programming languages.
This is done using the translation interface, where syntax of a new language is described with files, and the language is translated either to machine code, or another programming language which will later be compiled.

@@

assignment: `@lval identifier **` \
`@op '='` `@rval boolexpression | expression`
\end{verbatim}

@@

A transformer file is just a series of these transformations:
\begin{verbatim}
createreg [name]
// Copy an element from global multisymbol table to a 
//key in a register's multisymbol table
transfer(-append) [reg-name] [global-key] [reg-key] 
// Move the multisymbol from a register to the destination 
// key in the multisymbol table. 
// If a destination_reg is \
// specified, this table is the table of a register. 
// Otherwise, it is the global multisymbol table
pushback(-override) [reg-name] [destination] (optional)[destination_reg]
// Prefix for performing an operation on a register
reg [name] {command (any of below)}

// The following also work with operations on the 
// table of the current multisymbol
// In add and append, type might be "identifier" or "literal" 
//                              and value might be "x" or "2"
// I.e to add an identifier foo under the key "name", 
//   use the command (add name identifier foo)
// Add overwrites a key, append adds onto it.
add    [key] [type] [value]
append [key] [type] [value]
// Move deletes the source key, copy does not.
copy(-append) [key1] [key2]
move(-append) [key1] [key2]
// Change the tag of the register
retag newtag
// Delete a key from the multisymbol table
delete [key]
\end{verbatim}
Which can be surrounded by control flow, in the same way that constructor files can:
\begin{verbatim}
branch defined identifier 
move identifier old_identifier
add name identifier f
elsebranch
add name identifier f
end
\end{verbatim}
(This AST transform renames the syntax element to f, saving the old name to the key "old\_identifier"

@@

For example, adding a function to a particular programming language takes a single line:
\begin{verbatim}
function: 'def' `@name identifier **` '(' `@args sep ',' \
identifier **` ')' ':' `@body *statement` 'end'
\end{verbatim}
To change this Python style function to one in Haskell:
\begin{verbatim}
function: `@name identifier **` \
`@args sep SPACE identifier **` '=' `@body return` 'end'
\end{verbatim}
Since these two parsers define the same fields (name, args, body), they would be compiled in identical ways.
